Appendix A: Stochastic simulations of noisy phenomena

### 2017-10-27 appendixA/appendixA.Rmd
typo

## plot themes, non-essential
library(hrbrthemes)
library(ggthemes)
ggplot2::theme_set(hrbrthemes::theme_ipsum())
colours <- ptol_pal()(2)

>>>>

## plot themes, non-essential
library(ggthemes)
#library(hrbrthemes)
#ggplot2::theme_set(hrbrthemes::theme_ipsum())
ggplot2::theme_set(theme_bw())
colours <- ptol_pal()(2)
